### 2015-09-10 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Buildbot ran the code beautifier.
Change Axisem coupling Manual

\noindent Example :
\begin{verbatim}
input_box.txt
input_box_sem_cart.txt
32                          # number of AxiSEM mpi processes used in solver
90. 0.                      # source position (lat lon)
0.  60.                     # chunk center (lat lon)
1                           # number of axisem simus depends on moment tensor used
32                          # number of Specfem3D MPI processes
/[...]/example_1st_for_validation/MESH                          # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI    # Specfem databases dir
/[...]/example_1st_for_validation/DATA/AxiSEM_tractions/1       # AxiSEM tractions dir
\end{verbatim}

>>>>

\noindent Example :
\begin{verbatim}
input_box.txt
input_box_sem_cart.txt
32                          # number of AxiSEM mpi processes used in solver
90. 0.                      # source position (lat lon)
0.  60.  0.                 # chunk center (lat lon azi_rot)
1                           # number of axisem simus depends on moment tensor used
32                          # number of Specfem3D MPI processes
/[...]/example_1st_for_validation/MESH                          # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI    # Specfem databases dir
/[...]/example_1st_for_validation/DATA/AxiSEM_tractions/1       # AxiSEM tractions dir
\end{verbatim}
